Click chemistry reveals an alternate mechanism for HPII catalase

### 2018-02-20 bb494/manuscript.tex
b
add intro layout

@@

>>>>

\section{New Introduction}
Catalase is a

Understanding the optimizations of ubiquitous enzymes tells us how nature optimizes enzymes, and perhaps how faster-than-diffusion enzymes work
In particular, understanding how the long-range electric fields between two molecules might be used for biological purpose is interesting. Typically amino acids are quantified by their polarity, pka, bulk. E-field is a new mechanism of interest.
Catalase's tight perpendicular channel has a variety of optimizations:
   it evolved to concentrate H2O2 near its channel
   it is small, only allowing a couple solvent molecules through at once
   it uses two channels, one for reactant entrance and the other for product exit
   it uses hydrophobicity to prevent water from getting in, optimizing the H2O2 concentration in its heme pocket
   It uses an electric field to orient the chain of solvent molecules for optimal transmission and chemistry, even away from the heme

@@

An Electrical Potential in the Access Channel of Catalases Enhances Catalysis, loewen
An electrical gradient between Asp181 and the positive heme orients the waters in the pocket, promoting H-bonding and rotating H2O2 properly
